Rigidity of Expectation: Additional Evidence from Density Forecasts of Professionals and Households

### 2019-06-29 paper/Draft.tex
first typo cheacking. need to do it again after finalizing everything

\begin{abstract}
	Surveys on density forecasts of macroeconomic variable that are not available until recent dacade provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theoreis of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific regidity using uncertainty as the next step of analysis.

@@

Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade. This has been also engined by an incresingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.  On one hand, various theories built upon different micro foundations produce some similar macro patterns. For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.  On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.

This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probablistic forecast from both professional forecasters survey and household survey. Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models. But in the same time, the degree of rigidity apears to be shock-specific and bears the difference to households and professional forecasters.

The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if suveyees are asked to assign their perceived probabilities to a range of variables of the forecast. .\footnote{For an insightful survey on the importance of measuring subjective expectations using probablistic surveys, see \citet{manski2004measuring}.} With density forecasts. the variance of indivdual forecast can be estimated as an indicator of the uncertainty. Across different vintages of the forecast, the revsion in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.

@@

An agent $i$ is forming expectations about a stochastic variable $y^i_{t+h}$. The supscript $i$ can be dropped if it is an aggregate (i.e. inflation) variable instead of individual specific  (i.e. household income or house value). This paper focuses on forecasting of aggregate variables, in particular, inflation. So we can simply denote the variable as $y_{t+h}$. To put it another way, all agents are foreasting the same object. \footnote{Only in the context of forecasting aggregate variable, it is meaningful to study the average expectations and disagreements across agents.}

@@

$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instataneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \citet{xx}. }

@@

Similarly, individual forecasting variance $\sigma_{i,t+h|t}$, hereafter termed as indiviual uncertainty in this paper, is the conditional variance.

@@

Individual forecast error $FE_{i,t+h|t}$ is the difference of ex post realized value of $y_{t+h}$ and individual foreacast at time $t$.

@@

A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empricial tests of this kind include \citet{xx}.\citet{xx} etc. }

@@

As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized. So the uncertainty should drop unambigously.

An equivalent interpretation to this is through the perspective of revision. Defining the forecast revision as the difference of different vintages of foreacsts fixing the terminate date, the revision in uncertainty should be always negative and the drop should be exactly equal to discounted variance of the realized shocks. \footnote{Compared to other null hypotheses discussed above, this is a weaker test. It is true that rational foreacsting implies reduction in uncertainty with shorter horizon. But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE. }

@@

The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different microfoundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One of the most tractable models assume there is a homogenous Possion rate $\lambda$ of updating among the population. Specificaly, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

FIRE assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period. So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE. One can easily see that the reduction in ucnertainty is greater in SE for any $\tau>1$ than FIRE.

@@

It is important to note that the rigidity in updating according to SE cannot be systamatically observable in the individual level, both in terms of forecasts errors and uncertainty. This is because the behaviors of each individual foreacst specifically depends on if the she updates or not in that period.

@@

One well known prediction from SE literature is that the average foreacast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below. \footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$. Setting $\lambda=1$, then the SE collapses to FIRE and the average forecast is equal to $y$'s long-run mean of zero.

@@

Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibites serial correlation described as below in a similar spirt of forecast errors. It is equal to a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart. \footnote{Make sure you have clarify the difference between revision and change.}

@@

 In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$. The first component is the inefficiency sourced from stickiness of updating. The higher rigidity (lower $\lambda$), the smaller the efficieny gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.

@@

\begin{itemize}
\item Individual uncertainty need not unambiguously drop with shorter horizon. 
\item Population mean forecast paritially responds to shocks and with lags. 
\item Forecast errors are serially correlated. 
\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
\item Population average uncertaity revision is serially correlated and underreacts to volatility of the shocks.

@@

What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$. Specificaly, mean forecast of individual $i$ is the posterior mean of based on her prior and realized signals $s_i$.

@@

Now, the parameter that governs rigidity is $1-PH$. It is a function of priror uncertainty about $y$ and noisiness of the signals. It is time variant as the variance is updated by the agent each period.

@@

As in FIRE and SE, uncertainty itself does not depend upon the realization of the shocks or signals. The revision in uncertainy from time $t-1$ to $t$ fixing the terminate of the forecast date is negative  unambigously. To see this

@@

From $t$ to $t+1$, when $h\geq 1$, the decline in variance come from two sources. The first source is the pure gain from the new signals, i.e. $\Delta \Sigma^y_{i,t|t}$. It is scalled by the factor $\rho^{2h}$. The second source is present in full information rational expectation model: as time goes from $t-1$ to $t$, there is a reduction of uncertainty about $\omega_t$.

@@

One of the major implications from NI models is that both individual forecast and ucnertainty behaves the same pattern as population forecasts.

In parituclar, the same as indivdiual forecast erro, average forecast errors have serial correlation with the same auto regression parameter $\rho^h(1-PH)$.

As to the uncertainty, as it does not depend on realized signals and the precision is the same aross all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.

Also, same as the individual variance, the variance unambiguiously drop in each vintage of revision. But since the signal is noisy, agents partially react to the news and uncertainty does not drop as efficiently as FIRE.

@@

The disagreements increase as time goes from $t-1$ to $t$. Also, as the time approaches $t+h$, the disagreements increase. This seems counterintuitive. But the reason is that here the disagreenments always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.

@@

$\bullet$  Invididual expectation adjusts in each period, but only partially adjusts to new information. \\
$\bullet$ Unlike sticky expectation, slugishness in adjustment or serial correlation of adjustment exists in individual level. The correlation parameter decreases with forecast horizon, which is not the case in sticky expectation.\\
$\bullet$  Individual variance unambiguously drops each period as one approaches the period of realization. In sticky expectation, it increases regardless of updating or not. \\ 
$\bullet$  Population average forecast partially adjusts to news and has serial correlation as the individual level. \\
$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreetments will never be zero. \\
$\bullet$  Average variance declines unambiguously each period.

@@

Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts accroding to different theories. As we focus on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.

This is the most intuitively seen in the dynamics of uncertainty. In particular, as one appraoch the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.

@@

One of the common predictions of SE and NI is there is information rigidity or stickiness of expecatations.  But both theory have suble difference in implied rigidity. I illustrate this in Figure \ref{rigidity}. One notable difference is that SE's rigidty is exogeously fixed. NI's rigidity is endogeously determined by the noisiness of the signals and it is time varying.

@@

\subsection{Disucussion of other theories}

@@

\item Epidemiologic view. \citet{carroll2003macroeconomic} Regardless of the microfoundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

@@

The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both currenct year forecast and 1-year-ahead inflation foreacst each quarter.

@@

We follow \citet{engelberg2009comparing} to estiamte the density distribution of each individual surveyee for SPF. New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty. Therefore, I directly use them.

For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.   For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extream values. \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in totla.}

@@

Although the sheer magnitudes of the differences between professionals' moments and those of houseolds are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency. Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.

It is widely documented in literature \cite{xxx, xxx} and resonated by anecdotal narrative that high inflation is typically associated with high inflation uncertainty. However, the observable correlation of realized inflation and the directly estimated average uncertainty from both  forecasters and households are, if any, negative during the period between 2007-2019. In particular, the correlation coefficients are -0.1, -0.05 and -0.24 for SPF's  CPI forecast, SPF's PCE forecast and SCE's CPI expectation. This may suggest that during a period of persistently low inflation, the conventiaonl positive redux of inflation and uncertainty is not a good description of the relation of the two.

The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between forecast error and uncertainty. Although according to our benchmark frameowork in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors. The correlation coefficent of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, resptively. Compared to professional forecasts, households forecasts exhibit such a positive correlation.

 The last row in of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreements and uncertainty. Many empriical literature in macroecoomics use disagreements and uncertainty as if they are similar concepts. Partly this confusion in practice is due to difficulty of finding the appropriate measure of this in the first place. But as we have presented in \ref{theory}, the two are distinct concepts. The empricial pattern of the two,  as shown in the plots, also confirms that the two are different objects. The correlation coefficients of the two turn out to be negative, -0.29 and -0.46 for SPF forecasts. In stark contrast, households seem to bear a strong correlation of 0.62 between the two moments.

Overall, professional forecasters' moments exhibit patterns more consistency from a statistical point of view.  In constrast, the positive correlation across households' ex ante uncertainty, ex post forecat errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.

Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}. A similar fact checking can be done with respect to individual uncertaintiy. FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREInd}. In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}). NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precesion of signals and the same prior of uncertainty (Equation \ref{VarNIEq}). Therefore, precense of dispersion of uncertainty across agents can be read against FIRE.

Figure \ref{IQR_Unceratitny} plots the median inflation expectation along its 25/75 percentiles in the left and its counterpart in uncertainty in the righ coumn.  Not only there is long-lasting dispersion in individual forecasts, i.e. disagreements, but alslo notable heterogeneity in uncertainty across agents.  And not surprisingly, the dispersion of both forecasts and uncertainty of households are both of a much greater magnitude than that of the professionals. The 25/75 inter-quantile-range of households point forecasts is 4-5 percentage points compared to 1 percentage point of professionals. And the IQR of uncertainty of housheolds are around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.

Beside, there are cross-agent-type difference and similarity in terms of distribution of uncertainty. Households' uncertainty are more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty. This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernal density estimated distribution of uncertainty by year on. What is common for both types of agents is that the dispersion in uncertainty is persistent over time and do not show much time-variation.

Another pattern worth discussing in Figure \ref{IQR_Unceratitny} is that there is a notable rise in the dispersion of professional forecasts in the recent 2-3 years, primarily driven by an increase of upper side of the forecast (i.e. 75 percentile forecast increases from 1\% to 2\%). \footnote{This should be interpreted with causion since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exihibits a gradual decline. } This is consistent with the observation in top left two figures Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flatten.

FIRE also predicts an unambigous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks. Although quantitatively it is hard to check this, one can look if the distribution of the uncertainy revision concentrate in the negative range. Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty from 1-year-ahead forecast in year $t-1$ to the current-year nowcast in year $t$. The more negative range in which the revision lies, the more ``rational'' of the forecast. Looking from the histograms, uncertainty revision shows left-skewness relative to zero. This implies on average,  more forecasters feel more certain for her nowcast relative to her forecast made one year before.  Unfortunately, since SCE does not provide the data structure for this purpose, we cannot make a comparison between two types of agents. A formal test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.

@@

The first set of tests, hereafter, referred as FE-based tests, utilize the moment restrictions on forecast errors. In plain words, the null hypothesis of the three tests are the following. First, since the forecasts are on average unbiased according to FIRE, forecast errors across agents should converge to zero in large sample. Second, forecast errors of non-overlapping forecasting horizon are not serially correlated (Equation \ref{NoSerialCorrFE} ).  Third, forecast errors cannot be predicted by any information available at the time of forecast, including the mean forecast itself and other variable that is in the agent's information content. This follows from Equation \ref{NoPastInfFE}. In addition, I include what is called weak version of the FE-based test which explores the serial correlation of forecast erros in overlapping periods,  i.e. 1-year-ahead forecasts within one year. The forecast errors are correlated to the extent of the realized shocks in the overlapping periods. So the positve serial correlation does not direct violate FIRE. For this reason, looking into the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.

FE-based tests results are prensented in Table \ref{NullTestTable}. Individual level data are used thanks to the panel structure of both surveys. Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE. Also,the regresions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE. Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.

First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$. There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecaters(2.2 versus 0.12) for headline CPI.

>>>>

	\begin{abstract}
		Surveys on density forecasts of macroeconomic variable that are not available until recent two decades provides one additional moment restriction, uncertainty, for testing and exploring the implications of various theories on expectation formation. This paper first documents the persistent dispersion in uncertainty about future inflation across economists and households. Second,  utilizing the panel data of individual uncertainty, I provide additional test results and estimates that are not consistent with the benchmark prediction of full-information rational expectation (FIRE). Finally, using externally identified shocks to inflation, I show the dynamic responses of forecasting moments to shocks are broadly consistent with theories of expectation rigidity and points to evidence for shock-dependent nature of the rigidity.  This sets the stage for estimating shock-specific rigidity using uncertainty as the next step of analysis.

@@

	Theories on how agents form expectations in ways deviating from rational expectation(RE) have proliferated over the past decade. This has been also engined by an increasingly welcoming recognition of the use of surveys by macroeconomists in testing theories empirically.  On one hand, various theories built upon different micro foundations produce some similar macro patterns. For instance, the notion of information rigidity, or expectation rigidity could be micro founded by many different theories, but mostly generate sluggish response to new information.  On the other hand, there are important and subtle differences in testable predictions from these theories for both individual forecasts and aggregate moments of the forecasts.

	This paper extends the current literature in this front by deriving the testable predictions from various theories on uncertainty and empirically test them utilizing the previously ignored probabilistic forecast from both professional forecasters survey and household survey. Overall, the paper finds additional evidence from uncertainty consistent with the rigidity models. But in the same time, the degree of rigidity appears to be shock-specific and bears the difference to households and professional forecasters.

	The contributions of this paper primarily rely upon the additional insights from the forecast uncertainty, that is only available if surveyees are asked to assign their perceived probabilities to a range of variables of the forecast. .\footnote{For an insightful survey on the importance of measuring subjective expectations using probabilistic surveys, see \citet{manski2004measuring}.} With density forecasts. the variance of individual forecast can be estimated as an indicator of the uncertainty. Across different vintages of the forecast, the revision in uncertainty is a direct measure of  information gain or the degree of forecasting efficiency. Besides, as in a typical signal-extraction model, the prediction that new information reduce conditional variance can be tested only using probability distributions.

@@

	An agent $i$ is forming expectations about a stochastic variable $y^i_{t+h}$. The supscript $i$ can be dropped if it is an aggregate (i.e. inflation) variable instead of individual specific  (i.e. household income or house value). This paper focuses on forecasting of aggregate variables, in particular, inflation. So we can simply denote the variable as $y_{t+h}$. To put it another way, all agents are forecasting the same object. \footnote{Only in the context of forecasting aggregate variable, it is meaningful to study the average expectations and disagreements across agents.}

@@

	$I_{i,t}$ is the information set available for individual $i$ at time t. The information set can be  agent specific, thus it has subscript $i$.  The specific content contained in $I_t$ varies from different models of expectation. For instance, sticky expectation and rational inattention literature all assume that agents are not able to update new information instantaneously. So the information set may not contain the most recent realization of the variable of forecast $y_t$. \footnote{Given the same information set available to agents, different theories may also differ in the underlying models each agent use to form the conditional density of the variables by agent $i$. Examples of such include multi-prior or model uncertainty. \citet{xx}. }

@@

	Similarly, individual forecasting variance $\sigma_{i,t+h|t}$, hereafter termed as individual uncertainty in this paper, is the conditional variance.

@@

	Individual forecast error $FE_{i,t+h|t}$ is the difference of ex post realized value of $y_{t+h}$ and individual forecast at time $t$.

@@

	A corollary is that disagreements do not respond to realized shocks any any point of the time.  \footnote{Empirical tests of this kind include \citet{xx}.\citet{xx} etc. }

@@

	As the forecasting horizon decreases relative to a given future point of time, there is a pure efficiency gain or reduction in uncertainty as more and more shocks have realized. So the uncertainty should drop unambiguously.

	An equivalent interpretation to this is through the perspective of revision. Defining the forecast revision as the difference of different vintages of forecasts fixing the terminate date, the revision in uncertainty should be always negative and the drop should be exactly equal to discounted variance of the realized shocks. \footnote{Compared to other null hypotheses discussed above, this is a weaker test. It is true that rational forecasting implies reduction in uncertainty with shorter horizon. But there is no direct test if the drop in uncertainty is efficient enough so as to be consistent with FIRE. }

@@

	The theory of sticky expectation (\citet{xx}, \citet{xx} ), regardless of its different micro-foundations by various authors, builds upon the assumption that agents do not update information instantaneously as they do in FIRE. One of the most tractable models assume there is a homogenous Poisson rate $\lambda$ of updating among the population. Specifically, at any point of time $t$, each agent learns about the up-to-date realization of $y_t$ with probability of $\lambda$; otherwise, it forms the expectation based on the most recent up-to-date realization of $y_{t-\tau}$, where $\tau$ is the time experienced since previous update.

@@

	FIRE assumes  $\tau=1$ for all the agents and all the time, namely all agents' last update takes place in previous period. So setting $\tau =1$ in above equation gives the reduction in uncertainty in FIRE. One can easily see that the reduction in uncertainty is greater in SE for any $\tau>1$ than FIRE.

@@

	It is important to note that the rigidity in updating according to SE cannot be systematically observable in the individual level, both in terms of forecasts errors and uncertainty. This is because the behaviors of each individual forecast specifically depends on if the she updates or not in that period.

@@

	One well known prediction from SE literature is that the average forecast is a weighted average of update-to-date rational expectation and lagged average expectation as reproduced below. \footnote{See \citet{coibion2012can} or appendix of this paper for detailed steps.} It can be also expressed as a weighted average to all the past realizations of $y$. Setting $\lambda=1$, then the SE collapses to FIRE and the average forecast is equal to $y$'s long-run mean of zero.

@@

	Since not all agents incorporate the recent realized shocks, the revision in average uncertainty exhibits serial correlation described as below in a similar spirt of forecast errors. It is equal to a weighted average of the resolution of uncertainty from the most recent shocks and its lagged counterpart. \footnote{Make sure you have clarify the difference between revision and change.}

@@

	In particular, the second component is the information gain from most recent realization of the shock underweighted by $\lambda<1$. The first component is the inefficiency sourced from stickiness of updating. The higher rigidity (lower $\lambda$), the smaller the efficiency gain or uncertainty reduction from one vintage of forecast to the next compared to its FIRE correspondents.

@@

	\begin{itemize}
		\item Individual uncertainty need not unambiguously drop with shorter horizon. 
		\item Population mean forecast partially responds to shocks and with lags. 
		\item Forecast errors are serially correlated. 
		\item Population disagreements rise in response to new shocks and return to steady state level gradually. 
		\item Population average uncertainty revision is serially correlated and underreacts to volatility of the shocks.

@@

	What is different from FIRE is that the agent makes her best guess of $y_t$ using Kalman filtering at time $t$. Specifically, mean forecast of individual $i$ is the posterior mean of based on her prior and realized signals $s_i$.

@@

	Now, the parameter that governs rigidity is $1-PH$. It is a function of prior uncertainty about $y$ and noisiness of the signals. It is time variant as the variance is updated by the agent each period.

@@

	As in FIRE and SE, uncertainty itself does not depend upon the realization of the shocks or signals. The revision in uncertainty from time $t-1$ to $t$ fixing the terminate of the forecast date is negative  unambiguously. To see this

@@

	From $t$ to $t+1$, when $h\geq 1$, the decline in variance come from two sources. The first source is the pure gain from the new signals, i.e. $\Delta \Sigma^y_{i,t|t}$. It is scaled by the factor $\rho^{2h}$. The second source is present in full information rational expectation model: as time goes from $t-1$ to $t$, there is a reduction of uncertainty about $\omega_t$.

@@

	One of the major implications from NI models is that both individual forecast and uncertainty behaves the same pattern as population forecasts.

	In particular, the same as individual forecast error, average forecast errors have serial correlation with the same auto regression parameter $\rho^h(1-PH)$.

	As to the uncertainty, as it does not depend on realized signals and the precision is the same across all agents, average variance $\bar \Sigma_{t+h|t}$ is equal to the variance of each individual.

	Also, same as the individual variance, the variance unambiguously drop in each vintage of revision. But since the signal is noisy, agents partially react to the news and uncertainty does not drop as efficiently as FIRE.

@@

	The disagreements increase as time goes from $t-1$ to $t$. Also, as the time approaches $t+h$, the disagreements increase. This seems counterintuitive. But the reason is that here the disagreements always exist simply because agents receive private signals, this disagreements is actually amplified as time goes forward.

@@

	$\bullet$  Individual expectation adjusts in each period, but only partially adjusts to new information. \\
	$\bullet$ Unlike sticky expectation, sluggishness in adjustment or serial correlation of adjustment exists in individual level. The correlation parameter decreases with forecast horizon, which is not the case in sticky expectation.\\
	$\bullet$  Individual variance unambiguously drops each period as one approaches the period of realization. In sticky expectation, it increases regardless of updating or not. \\ 
	$\bullet$  Population average forecast partially adjusts to news and has serial correlation as the individual level. \\
	$\bullet$  Population disagreements rise in each period as time approaches the period of realization. Disagreements will never be zero. \\
	$\bullet$  Average variance declines unambiguously each period.

@@

	Figure \ref{ir_pop} plots the impulse responses of population moments of forecasts according to different theories. As we focus on the dynamics of revision as one approaches the terminate date, i.e. forecast of $y_{t+h}$ at $t$, $t+1$, $t+2$ till $t+h$ instead of forecasts with fixed horizon, i.e. $y_{t+h}$,$y_{t+h+1}$.

	This is the most intuitively seen in the dynamics of uncertainty. In particular, as one approach the realization $t+h$, uncertainty necessarily drop for FIRE and attains zero at the last period.

@@

	One of the common predictions of SE and NI is there is information rigidity or stickiness of expectations.  But both theories have subtle difference in implied rigidity. I illustrate this in Figure \ref{rigidity}. One notable difference is that SE's rigidity is exogenously fixed. NI's rigidity is endogenously determined by the noisiness of the signals and it is time varying.

@@

	\subsection{Discussion of other theories}

@@

		\item Epidemiological view. \citet{carroll2003macroeconomic} Regardless of the micro-foundations of the information rigidity, households infrequently get access to more rational-and-up-to-date expectations from professional forecasters with a poisson process.

@@

	The structure of SPF allows us to directly test efficiency in revision as for the surveyees are asked to provide both current year forecast and 1-year-ahead inflation forecast each quarter.

@@

	We follow \citet{engelberg2009comparing} to estimates the density distribution of each individual surveyee for SPF. New York Fed has followed the same procedures for SCE and directly provided their estimate of uncertainty. Therefore, I directly use them.

	For SPF, I drop the outliers of mean forecast and uncertainty estimates at both top and bottom one percentiles as these are typically abnormals that are due to measurement errors or other reasons.   For SCE, I drop top and bottom 5 percentile of mean forecasts and uncertainty as households mean forecast re inclined to give extreme values. \footnote{(For mean forecasts and uncertainty, respectively, this means dropping 6528 and 5096 observations, out of 68887 observations in total.}

@@

	Although the sheer magnitudes of the differences between professionals' moments and those of households are so big that a direct comparison of the two seems redundant, their respective within-agent-type correlation serves a ready checking device of some statistical consistency. Figure \ref{UnceratitnyOtherMoments} plots the population uncertainty against realized inflation,  forecast errors and disagreements in the first, second and third rows, respectively.

	It is widely documented in literature \cite{xxx, xxx} and resonated by anecdotal narrative that high inflation is typically associated with high inflation uncertainty. However, the observable correlation of realized inflation and the directly estimated average uncertainty from both  forecasters and households are, if any, negative during the period between 2007-2019. In particular, the correlation coefficients are -0.1, -0.05 and -0.24 for SPF's  CPI forecast, SPF's PCE forecast and SCE's CPI expectation. This may suggest that during a period of persistently low inflation, the conventional positive redux of inflation and uncertainty is not a good description of the relation of the two.

	The middle row of Figure \ref{UnceratitnyOtherMoments} looks into the relationship between forecast error and uncertainty. Although according to our benchmark framework in \ref{theory}, there is no mathematical correlation between the forecast errors and uncertainty as the former depends on the realized shocks and the later depends on the volatility of the shock, it is worth checking if in the data a greater ex ante uncertainty implies bigger ex post forecast errors. The correlation coefficient of the two are 0.13, 0.06 and 040 for SPF CPI forecasts, SPF PCE forecasts and SCE households forecasts, respectively. Compared to professional forecasts, households forecasts exhibit such a positive correlation.

	The last row in of Figure \ref{UnceratitnyOtherMoments} explores the relationship between disagreements and uncertainty. Many empirical literature in macroeconomics use disagreements and uncertainty as if they are similar concepts. Partly this confusion in practice is due to difficulty of finding the appropriate measure of this in the first place. But as we have presented in \ref{theory}, the two are distinct concepts. The empirical pattern of the two,  as shown in the plots, also confirms that the two are different objects. The correlation coefficients of the two turn out to be negative, -0.29 and -0.46 for SPF forecasts. In stark contrast, households seem to bear a strong correlation of 0.62 between the two moments.

	Overall, professional forecasters' moments exhibit patterns more consistency from a statistical point of view.  In contrast, the positive correlation across households' ex ante uncertainty, ex post forecast errors, and cross-section disagreements cannot be easily reconciled by the framework we set up in Section \ref{theory}.

	Persistent disagreements in expectations has been used as an important stylized evidence against the null of identical expectation assumption embedded in FIRE, for instance, \citet{mankiw2003disagreement}. A similar fact checking can be done with respect to individual uncertainty. FIRE predicts individual share equal degree of uncertainty as  seen in Equation \ref{VarREInd}. In contrast, SE predicts that uncertainty of individuals differ in that agents are not equally updated at a point of the time (Equation \ref{VarSEInd}). NI allows for possibility of homogeneity in uncertainty only under stringent condition of the equal precision of signals and the same prior of uncertainty (Equation \ref{VarNIEq}). Therefore, presence of dispersion of uncertainty across agents can be read against FIRE.

	Figure \ref{IQR_Unceratitny} plots the median inflation expectation along its 25/75 percentiles in the left and its counterpart in uncertainty in the right column.  Not only there is long-lasting dispersion in individual forecasts, i.e. disagreements, but also notable heterogeneity in uncertainty across agents.  And not surprisingly, the dispersion of both forecasts and uncertainty of households are both of a much greater magnitude than that of the professionals. The 25/75 inter-quantile-range of households point forecasts is 4-5 percentage points compared to 1 percentage point of professionals. And the IQR of uncertainty of households are around 150-200 times(12-14 times for standard deviation) as that of professional forecasters.

	Beside, there are cross-agent-type difference and similarity in terms of distribution of uncertainty. Households' uncertainty are more skewed toward to the right (higher uncertainty), meaning there is a wide dispersion in the high values of uncertainty. This can be also seen in Figure \ref{Unceratitny_Histogram}, where I plot the kernel density estimated distribution of uncertainty by year on. What is common for both types of agents is that the dispersion in uncertainty is persistent over time and do not show much time-variation.

	Another pattern worth discussing in Figure \ref{IQR_Unceratitny} is that there is a notable rise in the dispersion of professional forecasts in the recent 2-3 years, primarily driven by an increase of upper side of the forecast (i.e. 75 percentile forecast increases from 1\% to 2\%). \footnote{This should be interpreted with caution since the disagreements of SPF forecasts shown in bottom row of Figure \ref{UnceratitnyOtherMoments} actually exhibits a gradual decline. } This is consistent with the observation in top left two figures Figure \ref{Unceratitny_Histogram} that the distribution of inflation forecasts in recent years have become flatten.

	FIRE also predicts an unambiguous reduction in uncertainty as one approaches to the date of realization, where the drop is exactly equal to the volatility of the realized shocks. Although quantitatively it is hard to check this, one can look if the distribution of the uncertainty revision concentrate in the negative range. Figure \ref{RevisionHist} plots the average revision in mean forecasts and uncertainty from 1-year-ahead forecast in year $t-1$ to the current-year nowcast in year $t$. The more negative range in which the revision lies, the more ``rational'' of the forecast. Looking from the histograms, uncertainty revision shows left-skewness relative to zero. This implies on average,  more forecasters feel more certain for her nowcast relative to her forecast made one year before.  Unfortunately, since SCE does not provide the data structure for this purpose, we cannot make a comparison between two types of agents. A formal test of revision equal to zero or being negative will be carried out in the Section \ref{NullTest}.

@@

	The first set of tests, hereafter, referred as FE-based tests, utilize the moment restrictions on forecast errors. In plain words, the null hypothesis of the three tests are the following. First, since the forecasts are on average unbiased according to FIRE, forecast errors across agents should converge to zero in large sample. Second, forecast errors of non-overlapping forecasting horizon are not serially correlated (Equation \ref{NoSerialCorrFE} ).  Third, forecast errors cannot be predicted by any information available at the time of forecast, including the mean forecast itself and other variable that is in the agent's information content. This follows from Equation \ref{NoPastInfFE}. In addition, I include what is called weak version of the FE-based test which explores the serial correlation of forecast errors in overlapping periods,  i.e. 1-year-ahead forecasts within one year. The forecast errors are correlated to the extent of the realized shocks in the overlapping periods. So the positive serial correlation does not direct violate FIRE. For this reason, looking into the correlation of overlapping forecast errors still contain the useful information about the size of the realized shocks.

	FE-based tests results are presented in Table \ref{NullTestTable}. Individual level data are used thanks to the panel structure of both surveys. Since test 2 and 3 requires individual forecasts in vintages that are more than one year apart while SCE only surveys each household for 12 months, the two tests are done for only SPF forecasts of CPI and PCE. Also,the regressions are adjusted accordingly depending on the quarterly and monthly frequency of SPF and SCE. Since these regressions are based on 1-year inflations in overlapping periods, white standard error is computed for hypothesis testing.

	First,  all three forecast series easily reject the unbiasedness test in the significance level of $1\%$. There is upward bias across professional forecasters and households \footnote{\citet{coibion2018firms} finds the same upward bias for firms' managers.}, while unsurprisingly, the bias is almost 20 times of that for professional forecasters(2.2 versus 0.12) for headline CPI.
